### 2019-04-01 manuscript.tex
Update manuscript.tex

It is estimated, based on a UNICEF global database including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS),  and other nationally representative surveys between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East and 44 millions of them are girls below age 15 \cite{UNIC16}.  The United Nations has declared that FGC as violates human rights, and promoted the abandonment of the practice  \cite{WHO97, WHO08}.  Current progress in reducing FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next decade \cfonly{double check}) if the trends continue \cite{KhosBane17, UNIC16} (also see
\url{http://www.who.int/mediacentre/factsheets/fs241/en/} updated Sep, 18).  Breaking with the tradition can be salvaging even after migration \cite{CreiSamu19, PariSaru18, WahlJohn17a}.  FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01}  \cfonly{To rethink differences between FGC and FGM.  The types of FGC vary from just a knick to a sever sewing of the genital area.  Using FGC(cutting) seems to ignore the damage to the girls and human rights, but FGM(utilization) seem harsh and biased against local cultures.  FGC(cirumcision) may be the best for current situation globally.)

The commonly shared position for FGC is more about eradication than intervention \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}; but the
progress is hindered due to the complicated history of the very practice \cite{cite}. The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to cultural and religious identity in one end and to public health and human rights on the other \cite{Boyl02, KhosBane17, KimaShell18, SchuLien13, WHO12}.

Social norm is \cite{DuncWand11, EffeVogt15, Hayf05, Mack96, Mack00, Youn02} a fundamental approach in understanding FGC practice while human rights and feminist theory entails \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} and modernization theory \cite{BoylMcMo02, (see BellNova15 and Hayf05 for reference)}entails reasons of intervening and abolishing the practices.  Convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe09}.  FGC was also viewed as a social capital for inclusion and exclusion within women’s social groups \cite{Shel-Wand11}.  When norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92}; hence, intervention of FGC targeting women's social networks, which are intergenerational, interdependent and interconnected across generations and genders was proposed \cite{Mack00, DuncWand11, ShelWand11}.

There is a wide range of gender theories on FGC (see\cite{Anti13, Hodg11, Lewi95}) and woman's empowerment on making FGC decision are shared concerns: for example, from social position \cite{VanMeek15}, autonomy \cite{Meye00}, gender equality and human rights \cite{Drol11}, to gender identity \cite{Youn04, Koom14, WintKoom09}. Both convention theory and gender approaches centre on values of how FGC associates with identity \cte{cites}.  Although convention theory was well studied and showed a larger effect on FGC practices than the others (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), gender perspective can shed lights on how women’s gender values intertwine with convention theory of FGC values \cite{cites}.   Modernization theory proposed that, for example, education and \cite{BoylMcMo02, Youn02} can contribute to the reduction of FGC practice.  Multiple theoretical frameworks would have to be incorporated to grasp a full explanation of the persistence and decline of FGC due to the heterogeneity of the population \cite{Hayf05, EffeVogt15, ModrLiu13}.

@@

Identifying benefits of FGC practice is crucial to promote sustainable change \cite{EffeVogt15}.  This study takes both the dynamics of beliefs of FGC benefits and of intention of FGC practices into account at both a population and a community level to understand associations of FGC values and intention of carrying out the practices l \cite{BoylCorl010, Drol11,Hayf05, Grue05, Hodg11,KandNwak09, OdukAfol17} (to confirm).  We developed three models in this study.  The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and intention to cut daughters in the hope that if patterns of social norms (i.e., aggregation of values of FGC benefits) associating behavioral intention can be detected.  Additionally, we also decompose the model into two “structural” models:  “future” model to study women’s beliefs of FGC benefits and FGC continuance; and “futureDaughter” model to examine the association of beliefs of FGC benefits, FGC continuance and intention of cutting daughters to understand how such positions change the main model.

@@

% collective action problem referring to community level of impact
Attitude was the strongest predictor of mothers' intentions for their daughters' FGC status, followed by subjective norms \cite{PashPonn16}. It implied that community norm (social norm) was not as clear as suggested \cite{EffeVogt15}, but believed otherwise \cite{DuncWand11, Hayf06, Mack96, Mack00, Mack06, Youn02} (to confirm).

% The findig “suggests that even with a sharp decrease in FGC prevalence, the bulk of FGC persistence would still come from household-level factors. This is in contrast to the tipping point and informational cascade models … , wherein the decision to abandon a social norm such as FGC should be entirely individual in places where the practice is highly pervasive.” \cite{BellNova15}

@@

>>>>

It is estimated, based on a UNICEF global database including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS),  and other nationally representative surveys between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East and 44 millions of them are girls below age 15 \cite{UNIC16}.  Current progress in reducing FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next decade \cfonly{double check}) if the trends continue \cite{KhosBane17, UNIC16} (also see \url{http://www.who.int/mediacentre/factsheets/fs241/en/} updated Sep, 18).  FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01}  \cfonly{To rethink differences between FGC and FGM.  The types of FGC vary from just a knick to a sever sewing of the genital area.  Using FGC(cutting) seems to ignore the damage to the girls and human rights, but FGM(utilization) seem harsh and biased against local cultures.  FGC(cirumcision) may be the best for current situation globally.)

The commonly shared position for FGC is more about eradication than intervention \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}, as the United Nations has declared that FGC as violates human rights, and promoted the abandonment of the practice  \cite{WHO97, WHO08} \cfonly{add and update}.  The progress is hindered due to the complicated history of the very practice \cite{Cami16}. The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to cultural and religious identity in one end and to public health and human rights on the other \cite{Boyl02, KhosBane17, KimaShell18, SchuLien13, WHO12}.

Social norm is a fundamental approach in comprehending and intervening FGC practice \cite{DuncWand11, EffeVogt15, Hayf05, Mack96, Mack00, Youn02} while other perspectives (e.g., human rights and feminist theory \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} entails reasons of negotiating and abolishing the practices.  Convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe09}.  FGC was also viewed as a social capital for inclusion and exclusion within women’s social groups \cite{Shel-Wand11}.  When the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92} and the bond within women's social networks could be intergenerational, interdependent and interconnected across generations and genders was proposed intervention of FGC  \cite{Mack00, DuncWand11, ShelWand11}. \cfonly{add \cite{Bicc15}}

\cfonly{add \cite{AlcaGonz13, BellNova15, PashPonn16, more} and other norm studies of why mother cut daughters etc}

Although convention theory was well deliberated and applied and showed a larger effect on FGC practices than the others (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}),  it was not without challenges \cite{EffeVogt15} and multiple theoretical frameworks were called to be incorporated to grasp a full explanation of the persistence and decline of FGC due to the heterogeneity of the population \cite{EffeVogt15, ModrLiu13}.

@@

Identifying benefits of FGC practice is crucial to promote sustainable change \cite{EffeVogt15}.  This study takes both the dynamics of beliefs of FGC benefits and of FGC practices into account at both a population and a community level to understand associations of FGC values and intention of carrying out the practices l \cite{BoylCorl010, Drol11,Hayf05, Grue05, Hodg11,KandNwak09, OdukAfol17} (to confirm).  We developed three models in this study.  The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and intention to cut daughters in the hope that if patterns of social norms (i.e., aggregation of values of FGC benefits) associating behavioral intention can be detected.  Additionally, we also decompose the model into two “structural” models:  “persistence” model to study women’s beliefs of FGC benefits and FGC continuance; and “future” model to examine the association of beliefs of FGC benefits, FGC persistence and intention of cutting daughters to understand how such positions change the main model.

@@

% FGC laws in those nations
% collective action problem referring to community level of impact
Attitude was the strongest predictor of mothers' intentions for their daughters' FGC status, followed by subjective norms \cite{PashPonn16}. It implied that community norm (social norm) was not as clear as suggested \cite{EffeVogt15}, but believed otherwise \cite{DuncWand11, Hayf06, Mack96, Mack00, Mack06, Youn02} (to confirm).

% The findig “suggests that even with a sharp decrease in FGC prevalence, the bulk of FGC persistence would still come from household-level factors. This is in contrast to the tipping point and informational cascade models … , wherein the decision to abandon a social norm such as FGC should be entirely individual in places where the practice is highly pervasive.”  they found that “that much of the variation in a woman's support for FGC can be attributed to individual- and household-level factors rather than to village-level factors or to factors beyond the village level”  \cite{BellNova15}; and to compare our results to \cite{BellNova15} because they agnostic about the three theories.

@@

%There is a wide range of gender theories on FGC (see\cite{Anti13, Hodg11, Lewi95}) and woman's empowerment on making FGC decision are shared concerns: for example, from social position \cite{VanMeek15}, autonomy \cite{Meye00}, gender equality and human rights \cite{Drol11}, to gender identity \cite{Youn04, Koom14, WintKoom09}…..Modernization theory proposed that, for example, education and \cite{BoylMcMo02, Youn02} can contribute to the reduction of FGC practice.
